---
title: "Practical Machine Learning Project"
author: "Ed Yang"
date: "July 12, 2016"
data source: http://groupware.les.inf.puc-rio.br/har
---
## Background

Using wareable devices to find patterns in weight lifting exercise. Tester were asked to perform barbell lifts correctly and incorrectly in 5 different ways (A,B,C,D,E). 
The goal of this project is to predict the manner of the test subjects in which they did the exercise.

## Loading the data 

```{r warning=FALSE, comment=FALSE}
rm(list = ls())
if (!file.exists("pml-training.csv")) {
  download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", destfile = "pml-training.csv")
}
if (!file.exists("pml-testing.csv")) {
  download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", destfile = "pml-testing.csv")
}
traindata <- read.csv("pml-training.csv", sep = ",", na.strings = c("", "NA"))
testdata <- read.csv("pml-testing.csv", sep = ",", na.strings = c("", "NA"))
```

# Cleaning and spliting the data before learning

```{r warning=FALSE, comment=FALSE}
library(ggplot2)
library(lattice)
library(data.table)
library(caret)



cleaned <- names(traindata[,colSums(is.na(traindata)) == 0])[8:59]

#Claenout first seven columns because they do not have relationship with the prediction we are interested in, so we take them out of the training data set.


traindata <- traindata[,c(cleaned,"classe")]
testdata <- testdata[,c(cleaned,"problem_id")]


train_split <- createDataPartition(y=traindata$classe, p=0.7, list=FALSE)
mytrain <- traindata[train_split, ]
mytest <- traindata[-train_split, ]

```



## Learning Model

I’ll use Random Forest and Classification Tree model to do the prediction. 


```{r echo= FALSE, warning=FALSE, comment=FALSE}

set.seed(346)
library(randomForest)
modelrf <- randomForest(classe ~ ., data=mytrain)

modelct <- train(classe ~ ., data = mytrain, method="rpart")

#using RF model to test on my test data
prediction_rf <- predict(modelrf, mytest, type = "class")
prediction_ct <- predict(modelct, newdata=mytest)


#Analyse Confidence level using confusion Matrix on my test data

conf_mtx_rf <- confusionMatrix(prediction_rf, mytest$classe)
conf_mtx_ct <- confusionMatrix(prediction_ct, mytest$classe)
conf_mtx_rf
conf_mtx_ct

```


##Prediction using real test data

Since we thing the Random Forest methos confidence level is acceptable, we will use this model on test data

```{r warning=FALSE, comment=FALSE}
prediction_final <- predict(modelrf, testdata, type = "class")
prediction_final

```

##Conclusion
We can use the training data figure out a resonable model which is Random Forest within reasonable confidence. So we apply this model to the test data and got the above prediction.
